Holier Than Thou: Partisan Gap in the Consumption\\ of Pornography Online\thanks{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}.}

### 2023-01-08 ms/adult.tex
Update release
- Report sample sizes in results

- Add untruncated percentile splits by party for hours and percentage time spent on porn site

- Add regression tables for quantile and OLS regressions

- Add quantile regression results for piedomains classification

- Fix figures and tables caption

\author{Lucas Shen\thanks{Lucas is a Research Fellow at Asia Competitiveness Institute, Lee Kuan Yew School of Public Policy, at the National University of Singapore, \href{mailto:lucas@lucasshen.com}{\footnotesize{\texttt{lucas@lucasshen.com}}}} \and Gaurav Sood\thanks{Gaurav can be reached at \href{mailto:gsood07@gmail.com}{\footnotesize{\texttt{gsood07@gmail.com}}}}\vspace{.5cm}}

@@

Our data also includes characteristics of the respondents. We have data on demographic characteristics like birth year, state, gender, race, and education level. We also have information on their party identification. Except for 120 respondents who did not respond or picked ``not sure'' or ``don't know,'' the rest selected the party they identified with or marked themselves as independents. Of those 1,080 individuals, 82 percent lean either Republican or Democrat. The remaining 18 percent identify as independent.

@@

\subsection*{Consumption of Pornography}
Only about 32 percent of respondents consumed pornography online during the observation period. Of the 32\% of the respondents who consumed any pornography during the month, the median consumer consumed less than an hour of pornography while the 80th percentile consumer consumed nearly 4.5 hours and the 95th percentile, nearly 20 hours (see \cref{tab:distribution_duration}). You see a similar picture when it comes to the proportion of time spent online consuming pornography-the 50th percentile is nearly 3\%, the 80th percentile is about 14\%, and the 95th percentile is about 58\% (see \ref{tab:distribution_prop_duration}).

The consumption of pornography is also highly concentrated among a few sites, with the ten most frequented pornography sites receiving more than 12 times the traffic to all other pornographic sites (approximately 109 minutes vs. 9 minutes, see \cref{fig:concentration_porn_consumption}). Close to 80 percent of the traffic to pornographic sites is to just one pornographic site. Looking at the characteristics of consumers of pornography, expectedly, consumers of pornography online are younger and are more likely to be male (see, for instance, Panel B of \cref{tab:characteristics_split_by_porn_consumers}).

@@

Given the skew in the data, we ran a quantile regression, regressing the duration on party. As Figures \ref{fig:quantile_regression_duration}, the 80th percentile of the difference is close to 0 but from thereon, there is a sharp diverging trend with the 95th percentile difference nearly 1.5 hrs. For context, the 80th and 95th percentile of time spent on pornographic sites online among Republicans is nearly .3 hours and 6.2 hours respectively. In contrast, the corresponding numbers are .2 hours and 4.5 hours for Democrats.\footnote{

	We analyze the consumption of pornography online among independents in \cref{si:independents}. The median independent consumes more pornography than partisans (1.3 hours vs 0.7 hours in \cref{tab:percentiles_duration_adultsites_by_individuals_independents_partisans} and 3.4\% vs 2.3\% in \cref{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}). This pattern reverses somewhat near the right tail of the distribution.}

Looking at the percentage of time spent on pornographic sites reveals a similar trend to the trend in total time spent on pornographic sites (see \ref{fig:quantile_regression_prop_duration}). The 80th percentile of the partisan difference is nearly 0 and then there is a sharply rising line with differences nearly 10\% at the 100th percentile (albeit the number is very imprecisely estimated).

@@

To what extent are the results "explained" by the confounding demographic differences between the parties? To learn that, we control for immutable characteristics like age and gender. (\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.) We use these variables in our analyses of pornography consumption below. As Figure \ref{fig:quantile_regression_duration} shows, once you adjust for confounders, the partisan differences melt away.

%===========================

% Quantile regressions

% Hours spent on adult sites

%===========================

\begin{figure}[t]

	\centering

	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites}

	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}

	\caption*{\footnotesize \emph{Notes:}

		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.

		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.

		95\% confidence intervals constructed from standard errors.

		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.

	}

	\label{fig:quantile_regression_duration}

\end{figure}

%========================================

% Quantile regressions

% Proportion of time spent on adult sites

%========================================

\begin{figure}[t]

	\centering

	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites}

	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}

	\caption*{\footnotesize \emph{Notes:}

		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.

		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.

		95\% confidence intervals constructed from standard errors.

		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.

	}

	\label{fig:quantile_regression_prop_duration}

\end{figure}

\section*{Discussion}\label{sec:discussion}
\addcontentsline{toc}{section}{\nameref{sec:discussion}}
Consumption of pornography has been attributed to a variety of ills. It is also considered problematic from a religious perspective. For instance, Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}} The Internet has dramatically increased access to pornography. This has led to the concern that pornography consumption has become very widespread and extensive. Our data suggest that pornography consumption online is highly concentrated with very few people consuming a lot of pornography and most people consuming very little or none.

@@

\subsubsection{Skew in Website Visits}
%============================
% Figure of top 25 adultsites
%============================
\begin{figure}[ht]
	\centering
	\caption{Top 25 Pornography Sites}
	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows the top 25 pornographic sites that individuals visit in the sample period.
		Pornography sites are as categorized by YouGov (see the \nameref{sec:data} section).
		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  
		Sites to the right of the vertical dashed are the top 1 percent of pornographic sites.
	}
	\label{fig:top25_adult}
\end{figure}

%================================
% Figure of top 25 non-adultsites
%================================
\begin{figure}
	\centering
	\caption{Top 25 (Non-Porn) Domains}
	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows the top 25 non-pornographic sites that individuals visit in the sample period.
		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  			
		Sites to the right of the vertical dashed are the top 1 percent (of non-pornographic sites).
	}
	\label{fig:top25_nonadult}
\end{figure}

%=============================================
% Figure for concentration of porn consumption
%=============================================
\begin{figure}
	\centering
	\caption{Traffic to Top 10 Pornographic Sites}
	\includegraphics[width=.5\textwidth]{../figs/concentration_porn_consumption.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The Top 10 bar indicates traffic to the top 10 pornographic sites in the data (see \cref{fig:top25_adult}).
		The Others bar indicates traffic to all other pornographic sites outside of the top 10.
		The y-axis is the total time spent on pornographic sites, averaged across individuals.
		Time units is hours.
		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption}
\end{figure}

%====================================
% Figure of traffic to top x websites
%====================================
\begin{figure}
	\centering
	\caption{Traffic to Top x Pornographic Sites by Party}
	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows concentration of pornography consumption based on individuals' most frequented pornographic sites.
		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption_topX_by_party}
\end{figure}

\FloatBarrier
\subsubsection{Skew in Consumption of Pornographic Content}
%====================================================
% Tabulated percentiles of hours spent on adult sites
%====================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online}
	\label{tab:distribution_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		See \cref{tab:distribution_prop_duration} for the distribution in terms of percentage of time.
		%See \cref{fig:distribution_duration} for the plot.
	}
\end{table}

%=====================================================================
% Tabulated percentiles of proportion of duration spent on adult sites
%=====================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Time Spent on Pornographic Sites}
	\label{tab:distribution_prop_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{\% time}}\\
			\midrule
			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the percentage of time on pornography sites spent by individuals who consumed pornography in the sample period. 
		See \cref{tab:distribution_duration} for the distribution in terms of hours.
		%See \cref{fig:distribution_prop_duration} for the plot.
	}
\end{table}

\FloatBarrier
\clearpage
\subsection{Partisan Differences}
\subsubsection{Distribution of Differences}
%===========================================================================
% Tabulated splits by party and by percentiles for hours spent on adultsites
%===========================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online by Party}
	\label{tab:distribution_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		See \cref{tab:distribution_prop_duration_party} for the distribution in terms of percentage of time. 
		See \cref{tab:piedomains_distribution_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.005, rejecting the null that the Republican and Democrat distributions are the same.
		%See \cref{fig:distribution_duration_party} for the plot.
	}
\end{table}

%===============================================================================
% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
%===============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Time Spent on Pornographic Sites by Party}
	\label{tab:distribution_prop_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period. 
		See \cref{tab:distribution_duration_party} for the distribution in terms of percentage of time.
		See \cref{tab:piedomains_distribution_prop_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.025, rejecting the null that the Republican and Democrat distributions are the same at the 5\% level.
		%See \cref{fig:distribution_prop_duration_party} for the plot.
	}
\end{table}

\FloatBarrier
\clearpage
\subsubsection{Accounting for Confounders}
%==============================================================================
% Table for balance of porn consumption and individual characteristics by party
%==============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
	\caption{Differences in Pornography Consumption and Individual Characteristics by Party}
	\label{tab:characteristics_split_by_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_party.tex}\\
			%-------------------------------------------------------------------
			\cmidrule{2-8}
			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_covariates_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		Table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, Democratic individuals, and Republican individuals.
		Standard deviations and percentages in parentheses.
		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
		Given the skew in consumption of pornography, we also performed tests for difference in medians for the measures of pornography consumption by party (see \cref{tab:characteristics_split_by_party_medians}).
	}
\end{table}

>>>>

\author{Lucas Shen\thanks{Lucas is a Research Fellow at the National University of Singapore, \href{mailto:lucas@lucasshen.com}{\footnotesize{\texttt{lucas@lucasshen.com}}}} \and Gaurav Sood\thanks{Gaurav can be reached at \href{mailto:gsood07@gmail.com}{\footnotesize{\texttt{gsood07@gmail.com}}}}\vspace{.5cm}}

@@

Our data also includes characteristics of the respondents. We have data on demographic characteristics like birth year, state, gender, race, and education level. We also have information on their party identification. Except for 120 respondents who did not respond or picked ``not sure'' or ``don't know,'' the rest selected the party they identified with or marked themselves as independents. Of those 1,080 individuals, 82 percent lean either Republican or Democrat. The remaining 18 percent identify as independent. Column (3) of \cref{tab:characteristics_split_by_party} reports summary statistics.

@@

\subsection*{Consumption of Pornography}
Only about 32 percent of respondents consumed pornography online during the observation period. Of the 32\% of the respondents who consumed any pornography during the month, the median consumer consumed less than an hour of pornography while the 80th percentile consumer consumed nearly 4.5 hours and the 95th percentile, nearly 20 hours (see \cref{tab:distribution_duration}). You see a similar picture when it comes to the proportion of time spent online consuming pornography---the 50th percentile is nearly 3\%, the 80th percentile is about 14\%, and the 95th percentile is about 58\% (see \ref{tab:distribution_prop_duration}).

The consumption of pornography is also highly concentrated among a few sites, with the ten most frequented pornography sites receiving more than 12 times the traffic to all other pornographic sites (approximately 109 minutes vs. 9 minutes, see \cref{fig:concentration_porn_consumption}). Close to 80 percent of the traffic to pornographic sites is to just one pornographic site (\cref{fig:concentration_porn_consumption_topX_by_party}).

Looking at the characteristics of consumers of pornography in Panel B of \cref{tab:characteristics_split_by_porn_consumers}, expectedly, consumers of pornography online are younger and are more likely to be male. 
In addition, consumers of pornography are no different in terms of party identification. The mean in the 7-point scale in party identification is identical, with a mean of 3.6 and a standard deviation of 2.2, for both consumers and non-consumers of pornography. Treating party identification as subgroups (Republicans, Independents, Democrats) does not change this lack of difference in party identification between consumers and non-consumers (see also \cref{fig:consume_porn_yes_no}). This foreshadows the systematic lack of partisan differences in consumption of pornography online we find below.

@@

%===========================
% Quantile regressions
% Hours spent on adult sites
%===========================
\begin{figure}[t]
	\centering
	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites}
	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Sample includes 834 individuals identified as either Republicans or Democrats.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
		See \cref{tab:regtab_quantile_reg_duration_adult} for a numerical report of the estimates.
	}
	\label{fig:quantile_regression_duration}
\end{figure}

%========================================
% Quantile regressions
% Proportion of time spent on adult sites
%========================================
\begin{figure}[t]
	\centering
	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Sample includes 834 individuals identified as either Republicans or Democrats.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
		See \cref{tab:regtab_quantile_reg_proportion_duration_adult} for a numerical report of the estimates.
	}
	\label{fig:quantile_regression_prop_duration}
\end{figure}

Given the skew in the data, we ran a quantile regression, regressing the duration on party. As \cref{fig:quantile_regression_duration}, the 80th percentile of the difference is close to 0 but from thereon, there is a sharp diverging trend with the 95th percentile difference nearly 1.5 hrs. For context, the 80th and 95th percentile of time spent on pornographic sites online among Republicans is nearly .3 hours and 6.2 hours respectively. In contrast, the corresponding numbers are .2 hours and 4.5 hours for Democrats.\footnote{
We analyze the consumption of pornography online among independents in \cref{si:independents}. The median independent consumes more pornography than partisans (1.3 hours vs 0.7 hours in \cref{tab:percentiles_duration_adultsites_by_individuals_independents_partisans} and 3.4\% vs 2.3\% in \cref{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}). This pattern reverses somewhat near the right tail of the distribution.}

Looking at the percentage of time spent on pornographic sites reveals a similar trend to the trend in total time spent on pornographic sites (see \cref{fig:quantile_regression_prop_duration}). The 80th percentile of the partisan difference is nearly 0 and then there is a sharply rising line with differences nearly 10\% at the 100th percentile (albeit the number is very imprecisely estimated).

@@

To what extent are the results "explained" by the confounding demographic differences between the parties? To learn that, we control for immutable characteristics like age, gender, level of education qualification, race, and region. (\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.) We use these variables in our analyses of pornography consumption below. As \cref{si:confounders} shows, once you adjust for confounders, the partisan differences melt away.\footnote{Using an alternative machine learning classifier of domains in \cref{si:alternate_ways} and alternative measures of pornography consumption (using traffic to pornographic sites) in \cref{si:visits} does little to change our conclusions.}

\section*{Discussion}\label{sec:discussion}
\addcontentsline{toc}{section}{\nameref{sec:discussion}}
Consumption of pornography has been attributed to a variety of ills. It is also considered problematic from a religious perspective. For instance, Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}.} The Internet has dramatically increased access to pornography. This has led to the concern that pornography consumption has become very widespread and extensive. Our data suggest that pornography consumption online is highly concentrated with very few people consuming a lot of pornography and most people consuming very little or none.

@@

\subsubsection{Skew in Website Visits}
%============================
% Figure of top 25 adultsites
%============================
\begin{figure}[ht]
	\centering
	\caption{Top 25 Pornography Sites}
	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows the top 25 pornographic sites that individuals visit in the sample period using over 6 million internet browsing logs.
		Pornography sites are as categorized by YouGov (see the \nameref{sec:data} section).
		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  
		Sites to the right of the vertical dashed are the top 1 percent of pornographic sites.
		See \cref{fig:top25_nonadult} for top non-pornographic domains.
	}
	\label{fig:top25_adult}
\end{figure}

%================================
% Figure of top 25 non-adultsites
%================================
\begin{figure}
	\centering
	\caption{Top 25 (Non-Pornographic) Domains}
	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows the top 25 non-pornographic sites that individuals visit in the sample period using over 6 million internet browsing logs.
		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  			
		Sites to the right of the vertical dashed are the top 1 percent (of non-pornographic sites).
		See \cref{fig:top25_nonadult} for top non-pornographic domains.
	}
	\label{fig:top25_nonadult}
\end{figure}

%=============================================
% Figure for concentration of porn consumption
%=============================================
\begin{figure}
	\centering
	\caption{Traffic to Top 10 Pornographic Sites}
	\includegraphics[width=.5\textwidth]{../figs/concentration_porn_consumption.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The Top 10 bar indicates traffic to the top 10 pornographic sites in the data (see \cref{fig:top25_adult}).
		Observations are at the individual-domain level (N = 2,437) for pornography sites and individuals who consume pornography online.
		The Others bar indicates traffic to all other pornographic sites outside of the top 10.
		The y-axis is the total time spent on pornographic sites, averaged across individuals.
		Time units is hours.
		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption}
\end{figure}

%====================================
% Figure of traffic to top x websites
%====================================
\begin{figure}
	\centering
	\caption{Traffic to Top x Pornographic Sites by Party}
	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows concentration of pornography consumption based on individuals' most frequented pornographic sites.
		Observations are from the 256 individuals with party identification (Republicans or Democrats) who consume pornography online.
		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption_topX_by_party}
\end{figure}

\FloatBarrier
\subsubsection{Skew in Consumption of Pornographic Content}
%====================================================
% Tabulated percentiles of hours spent on adult sites
%====================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online}
	\label{tab:distribution_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period (n = 353). 
		See \cref{tab:distribution_prop_duration} for the distribution in terms of percentage of time.
		%See \cref{fig:distribution_duration} for the plot.
	}
\end{table}

%=====================================================================
% Tabulated percentiles of proportion of duration spent on adult sites
%=====================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Time Spent on Pornographic Sites}
	\label{tab:distribution_prop_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{\% time}}\\
			\midrule
			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the percentage of time on pornography sites spent by individuals who consumed pornography in the sample period (n = 353). 
		See \cref{tab:distribution_duration} for the distribution in terms of hours.
		%See \cref{fig:distribution_prop_duration} for the plot.
	}
\end{table}

\FloatBarrier
\clearpage
\subsection{Partisan Differences}
\subsubsection{Distribution of Differences}
%===========================================================================
% Tabulated splits by party and by percentiles for hours spent on adultsites
%===========================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online by Party}
	\label{tab:distribution_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		Sample includes 256 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
		See \cref{tab:distribution_prop_duration_party} for the distribution in terms of percentage of time. 
		See \cref{tab:distribution_duration_party_untruncated} including non-consumers of pornography.
		See \cref{tab:piedomains_distribution_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.005, rejecting the null that the Republican and Democrat distributions are the same.
		%See \cref{fig:distribution_duration_party} for the plot.
	}
\end{table}

%===============================================================================
% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
%===============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Time Spent on Pornographic Sites by Party}
	\label{tab:distribution_prop_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period. 
		Sample includes 256 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
		See \cref{tab:distribution_duration_party} for the distribution in terms of percentage of time.
		See \cref{tab:distribution_prop_duration_party_untruncated} including non-consumers of pornography.
		See \cref{tab:piedomains_distribution_prop_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.025, rejecting the null that the Republican and Democrat distributions are the same at the 5\% level.
		%See \cref{fig:distribution_prop_duration_party} for the plot.
	}
\end{table}

%===========================================================================
% Tabulated splits by party and by percentiles for hours spent on adultsites
% Full sample
%===========================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online by Party\\ (Including non-consumers)}
	\label{tab:distribution_duration_party_untruncated}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party_untruncated.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		Sample includes 834 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
		See \cref{tab:distribution_prop_duration_party} for the distribution in terms of percentage of time. 
		See \cref{tab:piedomains_distribution_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.37, rejecting the null that the Republican and Democrat distributions are the same.
		%See \cref{fig:distribution_duration_party} for the plot.
	}
\end{table}
